---
title: "Gaia DR3, NGC 6544"
output:
  html_document:
    df_print: paged
---

Rank the globular clusters in the table by the ease of separating the cluster members from the field stars, using the [Gaia DR3](https://www.cosmos.esa.int/web/gaia-users/archive/programmatic-access). 

Here is the first example: 
[NGC 6544](https://people.smp.uq.edu.au/HolgerBaumgardt/globular/fits/ngc6544.html). The database of each globular cluster can be explored [here](https://people.smp.uq.edu.au/HolgerBaumgardt/globular/).

Variables used: `source_id`, `ra`, `dec`, `parallax`, `pmra`, `pmdec` , `bp_rp`, `mh_gspphot`, `radial_velocity`, `phot_g_mean_mag`.

```{r}
ngc_6544 <- read.csv("1657065339571O-result.csv")
```

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(ggpubr)
```

#### Summary Statistics 

```{r}
summary(ngc_6544)
```

#### Model 1

a. Use `lm()` to regress ra on dec and save the regression as `model_1`.

```{r}
model_1 <- lm(ra ~ dec, data = ngc_6544)
```

b. Regression results from the first model using `summary()`.

An increase of one unit of dec is associated with an additional -0.22698 unit decrease in ra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_1)
```

c. Plot results from `model_1`.

```{r}
ggplot(data = model_1, aes(x = dec, y = ra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="ra", x="dec") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6544 %>%
  ggplot(aes(dec,ra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="ra", x="dec")
```

#### Model 2

a. Use `lm()` to regress pmra on pmdec and save the regression as `model_2`.

```{r}
model_2 <- lm(pmra ~ pmdec, data = ngc_6544)
```

b. Regression results from the second model using `summary()`.

An increase of one unit of pmdec is associated with an additional 0.058145 unit increase in pmra. This relationship is statistically significant at < 0.001.


```{r}
summary(model_2)
```

c. Plot results from `model_2`.

```{r}
ggplot(data = model_2, aes(x = pmdec, y = pmra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="pmra", x="pmdec") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6544 %>%
  ggplot(aes(pmdec,pmra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="pmra", x="pmdec") 
```

#### Model 3

a. Use `lm()` to regress phot_g_mean_mag on bp_rp and save the regression as `model_3`.

```{r}
model_3 <- lm(phot_g_mean_mag ~ bp_rp, data = ngc_6544)
```

b. Regression results from the third model using `summary()`.

An increase of one unit of bp_rp is associated with an additional -0.02021 unit decrease in phot_g_mean_mag. This relationship is statistically significant at < 1.


```{r}
summary(model_3)
```

c. Plot results from `model_3`.

```{r}
ggplot(data = model_3, aes(x = bp_rp, y = phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="phot_g_mean_mag", x="bp_rp") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6544 %>%
  ggplot(aes(bp_rp,phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="phot_g_mean_mag", x="bp_rp")
```

#### Metallicity Over Hydrogen

```{r}
ggplot(ngc_6544, aes(mh_gspphot)) +
  geom_histogram(bins = 30)
```


#### Radio Velocity

```{r}
ggplot(ngc_6544, aes(radial_velocity)) +
  geom_histogram()
```

# Gaia DR3, NGC 6553

```{r}
ngc_6553 <- read_csv("1657165215641O-result.csv")
```

#### Summary Statistics 

```{r}
summary(ngc_6553)
```

#### Model 4

a. Use `lm()` to regress ra on dec and save the regression as `model_4`.

```{r}
model_4 <- lm(ra ~ dec, data = ngc_6553)
```

b. Regression results from the fourth model using `summary()`.

An increase of one unit of dec is associated with an additional  0.64366 unit increase in ra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_4)
```

c. Plot results from `model_4`.

```{r}
ggplot(data = model_4, aes(x = dec, y = ra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="ra", x="dec") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6553 %>%
  ggplot(aes(dec,ra)) +
  geom_point(alpha=0.5, size= 2, color = 'blue') +
  labs(y="ra", x="dec")
```

#### Model 5

a. Use `lm()` to regress pmra on pmdec and save the regression as `model_5`.

```{r}
model_5 <- lm(phot_g_mean_mag ~ bp_rp, data = ngc_6553)
```

b. Regression results from the fifth model using `summary()`.

An increase of one unit of pmdec is associated with an additional -1.8339 unit decrease in pmra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_5)
```

c. Plot results from `model_5`.

```{r}
ggplot(data = model_5, aes(x = bp_rp, y = phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="phot_g_mean_mag", x="bp_rp") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6553 %>%
  ggplot(aes(bp_rp,phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="phot_g_mean_mag", x="bp_rp")
```


#### Metallicity Over Hydrogen

```{r}
ggplot(ngc_6553, aes(mh_gspphot)) +
  geom_histogram(bins = 30)
```

#### Radio Velocity


```{r}
ggplot(ngc_6553, aes(radial_velocity)) +
  geom_histogram(bins = 30)
```

# Gaia DR3, Terzan 12


```{r}
terzan_12 <- read_csv("1657165792389O-result.csv")
```

#### Summary Statistics 

```{r}
summary(terzan_12)
```

#### Model 6

a. Use `lm()` to regress ra on dec and save the regression as `model_6`.

```{r}
model_6 <- lm(ra ~ dec, data = terzan_12)
```

b. Regression results from the first model using `summary()`.

An increase of one unit of dec is associated with an additional 0.01603 unit increase in ra. This relationship is statistically significant at < 1.

```{r}
summary(model_6)
```

c. Plot results from `model_6`.

```{r}
ggplot(data = model_6, aes(x = dec, y = ra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="ra", x="dec") +
  stat_smooth()
```

#### Graph 

```{r}
terzan_12 %>%
  ggplot(aes(dec,ra)) +
  geom_point(alpha=0.5, size= 2, color = 'blue') +
  labs(y="ra", x="dec")
```

#### Model 7

a. Use `lm()` to regress pmra on pmdec and save the regression as `model_7`.

```{r}
model_7 <- lm(pmra ~ pmdec, data = terzan_12)
```

b. Regression results from the second model using `summary()`.

An increase of one unit of pmdec is associated with an additional 0.17153 unit increase in pmra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_7)
```

c. Plot results from `model_7`.

```{r}
ggplot(data = model_7, aes(x = pmdec, y = pmra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="pmra", x="pmdec") +
  stat_smooth()
```

#### Graph 

```{r}
terzan_12 %>%
  ggplot(aes(pmdec,pmra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="pmra", x="pmdec") 
```

#### Metallicity Over Hydrogen

```{r}
ggplot(terzan_12, aes(mh_gspphot)) +
  geom_histogram(bins = 30)
```

#### Radio Velocity


```{r}
ggplot(terzan_12, aes(radial_velocity)) +
  geom_histogram(bins = 30)
```

# Gaia DR3, NGC 6380

```{r}
ngc_6380 <- read_csv("1657166932125O-result.csv") 
```

#### Summary Statistics 

```{r}
summary(ngc_6380)
```

#### Model 8

a. Use `lm()` to regress ra on dec and save the regression as `model_8`.

```{r}
model_8 <- lm(ra ~ dec, data = ngc_6380)
```

b. Regression results from the first model using `summary()`.

An increase of one unit of dec is associated with an additional 0.35053 unit increase in ra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_8)
```

c. Plot results from `model_8`.

```{r}
ggplot(data = model_8, aes(x = dec, y = ra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="ra", x="dec") +
  stat_smooth()
```

#### Graph 

```{r}
ngc_6380 %>%
  ggplot(aes(dec,ra)) +
  geom_point(alpha=0.5, size= 2, color = 'blue') +
  labs(y="ra", x="dec")
```

#### Model 9


a. Use `lm()` to regress pmra on pmdec and save the regression as `model_9`.

```{r}
model_9 <- lm(pmra ~ pmdec, data = ngc_6380)
```

b. Regression results from the second model using `summary()`.

An increase of one unit of pmdec is associated with an additional 0.17272 unit increase in pmra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_9)
```

c. Plot results from `model_9`.

```{r}
ggplot(data = model_9, aes(x = pmdec, y = pmra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="pmra", x="pmdec") +
  stat_smooth()
```

#### Graph

```{r}
ngc_6380 %>%
  ggplot(aes(pmdec,pmra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="pmra", x="pmdec") 
```

#### Model 10

a. Use `lm()` to regress phot_g_mean_mag on bp_rp and save the regression as `model_10`.

```{r}
model_10 <- lm(phot_g_mean_mag ~ bp_rp, data = ngc_6380)
```


b. Regression results from the third model using `summary()`.

An increase of one unit of bp_rp is associated with an additional -1.02741 unit decrease in phot_g_mean_mag. This relationship is statistically significant at < 0.001.

```{r}
summary(model_10)
```

c. Plot results from `model_10`.

```{r}
ggplot(data = model_10, aes(x = bp_rp, y = phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="phot_g_mean_mag", x="bp_rp") +
  stat_smooth()
```

#### Graph

```{r}
ngc_6380 %>%
  ggplot(aes(bp_rp,phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="phot_g_mean_mag", x="bp_rp")
```

#### Metallicity Over Hydrogen

```{r}
ggplot(ngc_6380, aes(mh_gspphot)) +
  geom_histogram(bins = 30)
```

#### Radio Velocity

```{r}
ggplot(ngc_6380, aes(radial_velocity)) +
  geom_histogram(bins = 30)
```

# Gaia DR3, FSR 1758

```{r}
fsr_1758 <- read.csv("1657248340808O-result.csv")
```

#### Summary Statistics

```{r}
summary(fsr_1758)
```

#### Model 11

a. Use `lm()` to regress ra on dec and save the regression as `model_11`.

```{r}
model_11 <- lm(ra ~ dec, data = fsr_1758)
```

b. Regression results from the first model using `summary()`.

An increase of one unit of dec is associated with an additional 0.59648 unit increase in ra. This relationship is statistically significant at < 0.001.

```{r}
summary(model_11)
```

c. Plot results from `model_11`.

```{r}
ggplot(data = model_11, aes(x = dec, y = ra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="ra", x="dec") +
  stat_smooth()
```

#### Graph

```{r}
fsr_1758 %>%
  ggplot(aes(dec,ra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="ra", x="dec")
```

#### Model 12

a. Use `lm()` to regress pmra on pmdec and save the regression as `model_12`.

```{r}
model_12 <- lm(pmra ~ pmdec, data = fsr_1758)
```

b. Regression results from the second model using `summary()`.

An increase of one unit of pmdec is associated with an additional 0.04283 unit increase in pmra. This relationship is statistically significant at < 0.1.

```{r}
summary(model_12)
```

c. Plot results from `model_12`.

```{r}
ggplot(data = model_12, aes(x = pmdec, y = pmra)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="pmra", x="pmdec") +
  stat_smooth()
```

#### Graph

```{r}
fsr_1758 %>%
  ggplot(aes(pmdec,pmra)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="pmra", x="pmdec") 
```

#### Model 13

a. Use `lm()` to regress phot_g_mean_mag on bp_rp and save the regression as `model_13`.

```{r}
model_13 <- lm(phot_g_mean_mag ~ bp_rp, data = fsr_1758)
```

b. Regression results from the third model using `summary()`.

An increase of one unit of bp_rp is associated with an additional -0.44855 unit decrease in phot_g_mean_mag. This relationship is statistically significant at < 0.001.

```{r}
summary(model_13)
```

c. Plot results from `model_13`.

```{r}
ggplot(data = model_13, aes(x = bp_rp, y = phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'orange') +
  labs(y="phot_g_mean_mag", x="bp_rp") +
  stat_smooth()
```

#### Graph 

```{r}
fsr_1758 %>%
  ggplot(aes(bp_rp,phot_g_mean_mag)) +
  geom_point(alpha=0.5, size=2, color = 'blue') +
  labs(y="phot_g_mean_mag", x="bp_rp")
```

#### Metallicity Over Hydrogen

```{r}
ggplot(fsr_1758, aes(mh_gspphot)) +
  geom_histogram(bins = 30)
```

#### Radio Velocity

```{r}
ggplot(fsr_1758, aes(radial_velocity)) + 
  geom_histogram(bins = 30)
```
```

